Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-01-15 paper/ms.tex

>>>>

In Section~\ref{sec:ref_frame}, we describe the general impact coordinate
system errors have on the measured actions. In Section~\ref{sec:local_fire},
we measure the local midplane in cosmological zoom-in simulations from the
FIRE collaboration. In Section~\ref{sec:discussion} we discuss and give some
context for our results, and implications for the definition of the Solar
neighborhood. We conclude in Section~\ref{sec:conclusion}.
